Correlation between photons emitted in different channels from an atom inside a leaky driven cavity

### 2021-08-11 newpaper.tex
Un par de errores ortograficos

\title{Correlation between photons emitted in diferent channels from
  an atom inside a leaky driven cavity}% Force line breaks with \\

@@

\begin{acknowledgments}
This work was supported by DGAPA-UNAM under grant PAPIIT-IG120518.
\end{acknowledgments}

>>>>

\title{Correlation between photons emitted in different channels from
  an atom inside a leaky driven cavity}% Force line breaks with \\

@@

\begin{acknowledgement}
This work was supported by DGAPA-UNAM under grant PAPIIT-IG120518.
\end{acknowledgement}
